---
title: "Selecting Features of GR Signaling that Predict Ligand-dependent Activity Profiles"
author: "Jerome C. Nwachukwu"
date: "5/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Load the package
library(randomForest)
library(Boruta)
library(pheatmap)
library(RColorBrewer)
library(grid)

#Set working directory
setwd("/Volumes/nettleslab/Jerome/Skeletal Muscle Data/Machine_learning/MARCONI/Boruta_with_GR_nuc_translocation_data/")
# Load and view the data
NanostringData <-read.csv("GR_data_wo_NR0s.csv", stringsAsFactors=TRUE)
# View(NanostringData)
rownames(NanostringData) <- NanostringData$Compound
NanostringData <- NanostringData[,-1]
NanostringData <- data.frame(scale(NanostringData))

# Cluster each type of feature separately and format the data
HTassays <- NanostringData[,c(1:7)]
Col.order <- hclust(dist(t(HTassays)))$order
HTassays <- HTassays[,Col.order]
HTassays <- cbind(rownames(HTassays), data.frame(HTassays, row.names=NULL))
colnames(HTassays)[colnames(HTassays)=="rownames(HTassays)"] <- "Compounds"
head(HTassays)

Peptides <- NanostringData[,c(8:154)]
Col.order <- hclust(dist(t(Peptides)))$order
Peptides <- Peptides[,Col.order]
Peptides <- cbind(rownames(Peptides), data.frame(Peptides, row.names=NULL))
colnames(Peptides)[colnames(Peptides)=="rownames(Peptides)"] <- "Compounds"
head(Peptides[,c(1:5)])

TargetGenes <- NanostringData[,c(155:187)]
Col.order <- hclust(dist(t(TargetGenes)))$order
TargetGenes <- TargetGenes[,Col.order]
TargetGenes <- cbind(rownames(TargetGenes), data.frame(TargetGenes, row.names=NULL))
colnames(TargetGenes)[colnames(TargetGenes)=="rownames(TargetGenes)"] <- "Compounds"
head(TargetGenes[,c(1:5)])

# Re-combine the datasets
myData <- merge(HTassays, Peptides, by = intersect(names(HTassays),names(Peptides)), by.x= 'Compounds', by.y= 'Compounds', all= FALSE, sort=TRUE)
myData <- merge(myData, TargetGenes, by = intersect(names(myData),names(TargetGenes)), by.x= 'Compounds', by.y= 'Compounds', all= FALSE, sort=TRUE)
row.names(myData) <- myData$Compounds
NanostringData <- myData[,-1]
#=============================
## Cluster the compounds
# Pick colors for the heatmap
# mycolors <-brewer.pal(10,"RdBu")
# mycolors # shows the colors, which are then used in reverse order below
mycolors <- c("#053061","#2166AC","#4393C3","#92C5DE","#D1E5F0", "#FDDBC7","#F4A582","#D6604D","#B2182B","#67001F")

# Set the color range of the heatmap
palette.break1 <- seq(-5, -1, 1)
palette.break2 <- seq(-0.9, 0, 0.25)
palette.break3 <- seq(0.1, 0.9, 0.25)
palette.break4 <- seq(1, 5, 1)
palette.breaksSUM <- c(palette.break1,palette.break2,palette.break3,palette.break4)
color.palette  <- colorRampPalette(mycolors)(length(palette.breaksSUM))

# Overwrite default draw_colnames in the pheatmap package.
draw_colnames_45 <- function (coln, gaps, ...) {
    coord <- pheatmap:::find_coordinates(length(coln), gaps)
    x     <- coord$coord - 0.5 * coord$size
    res   <- grid::textGrob(
      coln, x = x, y = unit(1, "npc") - unit(3,"bigpts"),
      vjust = 0.75, hjust = 1, rot = 90, gp = grid::gpar(...)
    )
    return(res)
}
assignInNamespace(
  x = "draw_colnames",
  value = "draw_colnames_45",
  ns = asNamespace("pheatmap")
)
# Plot heatmap. To separate the assay types change set "cluster_rows = F" and "gaps_row = c(7,154)"
pheatmap((t(NanostringData)),
          color = color.palette, border_color = "grey50",
          cellwidth = 6, cellheight = 2.5, 
          fontsize = 2.5, show_rownames = T,
          cluster_rows = T, cluster_cols = T, cutree_rows=4,
         gaps_col = 0, gaps_row = 0,
         main = "Clustering", breaks = palette.breaksSUM)

#===============================
# Determine the Predictors of Glut4 Translocation using Boruta
set.seed(104)
Glut4_boruta_104 <- Boruta(Glut4~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
Glut4_stats_104 <- attStats(Glut4_boruta_104)
Glut4_stats_104 <- Glut4_stats_104[order(Glut4_stats_104$'normHits', decreasing = T),]
head(Glut4_stats_104)
sink("Glut4_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Glut4_boruta_104)],NanostringData$Glut4))
sink()

# Change the random seed and repeat
set.seed(392)
Glut4_boruta_392 <- Boruta(Glut4~.,data=NanostringData, doTrace=2)
Glut4_stats_392 <- attStats(Glut4_boruta_392)
Glut4_stats_392 <- Glut4_stats_392[order(Glut4_stats_392$'normHits', decreasing = T),]
head(Glut4_stats_392)
sink("Glut4_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Glut4_boruta_392)],NanostringData$Glut4))
sink()

# Change the random seed and repeat
set.seed(426)
Glut4_boruta_426 <- Boruta(Glut4~.,data=NanostringData, doTrace=2)
Glut4_stats_426 <- attStats(Glut4_boruta_426)
Glut4_stats_426 <- Glut4_stats_426[order(Glut4_stats_426$'normHits', decreasing = T),]
head(Glut4_stats_426)
sink("Glut4_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Glut4_boruta_426)],NanostringData$Glut4))
sink()

# Combine results
colnames(Glut4_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(Glut4_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(Glut4_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

Glut4_stats <- merge(Glut4_stats_104,Glut4_stats_392, by = intersect(names(Glut4_stats_104),names(Glut4_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Glut4_stats) <- Glut4_stats$'Row.names'
Glut4_stats <- Glut4_stats[-1]
Glut4_stats <- merge(Glut4_stats,Glut4_stats_426, by = intersect(names(Glut4_stats),names(Glut4_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Glut4_stats) <- Glut4_stats$'Row.names'
Glut4_stats <- Glut4_stats[-1]
Glut4_stats <- Glut4_stats[order(Glut4_stats$'normHits_104', decreasing = T),]
head(Glut4_stats[1:6])

# Export results
write.csv (Glut4_stats, file="Glut4_Boruta.csv")

#===============================
# Determine the Predictors of GR Nuclear Translocation using Boruta
set.seed(104)
Nuc_boruta_104 <- Boruta(GR_Nuc_Trans~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
Nuc_stats_104 <- attStats(Nuc_boruta_104)
Nuc_stats_104 <- Nuc_stats_104[order(Nuc_stats_104$'normHits', decreasing = T),]
head(Nuc_stats_104)
sink("Nuc_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Nuc_boruta_104)],NanostringData$GR_Nuc_Trans))
sink()

# Change the random seed and repeat
set.seed(392)
Nuc_boruta_392 <- Boruta(GR_Nuc_Trans~.,data=NanostringData, doTrace=2)
Nuc_stats_392 <- attStats(Nuc_boruta_392)
Nuc_stats_392 <- Nuc_stats_392[order(Nuc_stats_392$'normHits', decreasing = T),]
head(Nuc_stats_392)
sink("Nuc_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Nuc_boruta_392)],NanostringData$GR_Nuc_Trans))
sink()

# Change the random seed and repeat
set.seed(426)
Nuc_boruta_426 <- Boruta(GR_Nuc_Trans~.,data=NanostringData, doTrace=2)
Nuc_stats_426 <- attStats(Nuc_boruta_426)
Nuc_stats_426 <- Nuc_stats_426[order(Nuc_stats_426$'normHits', decreasing = T),]
head(Nuc_stats_426)
sink("Nuc_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Nuc_boruta_426)],NanostringData$GR_Nuc_Trans))
sink()

# Combine results
colnames(Nuc_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(Nuc_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(Nuc_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

Nuc_stats <- merge(Nuc_stats_104,Nuc_stats_392, by = intersect(names(Nuc_stats_104),names(Nuc_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Nuc_stats) <- Nuc_stats$'Row.names'
Nuc_stats <- Nuc_stats[-1]
Nuc_stats <- merge(Nuc_stats,Nuc_stats_426, by = intersect(names(Nuc_stats),names(Nuc_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Nuc_stats) <- Nuc_stats$'Row.names'
Nuc_stats <- Nuc_stats[-1]
Nuc_stats <- Nuc_stats[order(Nuc_stats$'normHits_104', decreasing = T),]
head(Nuc_stats[1:6])

# Export results
write.csv (Nuc_stats, file="Nuc_Boruta.csv")

#===============================
# Determine the Predictors of Protein Synthesis using Boruta
set.seed(104)
Synthesis_boruta_104 <- Boruta(Synthesis~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
Synthesis_stats_104 <- attStats(Synthesis_boruta_104)
Synthesis_stats_104 <- Synthesis_stats_104[order(Synthesis_stats_104$'normHits', decreasing = T),]
head(Synthesis_stats_104)
sink("Synthesis_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Synthesis_boruta_104)],NanostringData$Synthesis))
sink()

# Change the random seed and repeat
set.seed(392)
Synthesis_boruta_392 <- Boruta(Synthesis~.,data=NanostringData, doTrace=2)
Synthesis_stats_392 <- attStats(Synthesis_boruta_392)
Synthesis_stats_392 <- Synthesis_stats_392[order(Synthesis_stats_392$'normHits', decreasing = T),]
head(Synthesis_stats_392)
sink("Synthesis_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Synthesis_boruta_392)],NanostringData$Synthesis))
sink()

# Change the random seed and repeat
set.seed(426)
Synthesis_boruta_426 <- Boruta(Synthesis~.,data=NanostringData, doTrace=2)
Synthesis_stats_426 <- attStats(Synthesis_boruta_426)
Synthesis_stats_426 <- Synthesis_stats_426[order(Synthesis_stats_426$'normHits', decreasing = T),]
head(Synthesis_stats_426)
sink("Synthesis_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Synthesis_boruta_426)],NanostringData$Synthesis))
sink()

# Combine results
colnames(Synthesis_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(Synthesis_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(Synthesis_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

Synthesis_stats <- merge(Synthesis_stats_104,Synthesis_stats_392, by = intersect(names(Synthesis_stats_104),names(Synthesis_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Synthesis_stats) <- Synthesis_stats$'Row.names'
Synthesis_stats <- Synthesis_stats[-1]
Synthesis_stats <- merge(Synthesis_stats,Synthesis_stats_426, by = intersect(names(Synthesis_stats),names(Synthesis_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Synthesis_stats) <- Synthesis_stats$'Row.names'
Synthesis_stats <- Synthesis_stats[-1]
Synthesis_stats <- Synthesis_stats[order(Synthesis_stats$'normHits_104', decreasing = T),]
head(Synthesis_stats[1:6])

# Export results
write.csv (Synthesis_stats, file="Synthesis_Boruta.csv")

#===============================
# Determine the Predictors of Protein Degradation using Boruta
set.seed(104)
Degradation_boruta_104 <- Boruta(Degradation~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
Degradation_stats_104 <- attStats(Degradation_boruta_104)
Degradation_stats_104 <- Degradation_stats_104[order(Degradation_stats_104$'normHits', decreasing = T),]
head(Degradation_stats_104)
sink("Degradation_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Degradation_boruta_104)],NanostringData$Degradation))
sink()

# Change the random seed and repeat
set.seed(392)
Degradation_boruta_392 <- Boruta(Degradation~.,data=NanostringData, doTrace=2)
Degradation_stats_392 <- attStats(Degradation_boruta_392)
Degradation_stats_392 <- Degradation_stats_392[order(Degradation_stats_392$'normHits', decreasing = T),]
head(Degradation_stats_392)
sink("Degradation_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Degradation_boruta_392)],NanostringData$Degradation))
sink()

# Change the random seed and repeat
set.seed(426)
Degradation_boruta_426 <- Boruta(Degradation~.,data=NanostringData, doTrace=2)
Degradation_stats_426 <- attStats(Degradation_boruta_426)
Degradation_stats_426 <- Degradation_stats_426[order(Degradation_stats_426$'normHits', decreasing = T),]
head(Degradation_stats_426)
sink("Degradation_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Degradation_boruta_426)],NanostringData$Degradation))
sink()

# Combine results
colnames(Degradation_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(Degradation_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(Degradation_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

Degradation_stats <- merge(Degradation_stats_104,Degradation_stats_392, by = intersect(names(Degradation_stats_104),names(Degradation_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Degradation_stats) <- Degradation_stats$'Row.names'
Degradation_stats <- Degradation_stats[-1]
Degradation_stats <- merge(Degradation_stats,Degradation_stats_426, by = intersect(names(Degradation_stats),names(Degradation_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Degradation_stats) <- Degradation_stats$'Row.names'
Degradation_stats <- Degradation_stats[-1]
Degradation_stats <- Degradation_stats[order(Degradation_stats$'normHits_104', decreasing = T),]
head(Degradation_stats[1:6])

# Export results
write.csv (Degradation_stats, file="Degradation_Boruta.csv")

#===============================
# Determine the Predictors of Mitochondrial Potential using Boruta
set.seed(104)
Mito_boruta_104 <- Boruta(Mito~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
Mito_stats_104 <- attStats(Mito_boruta_104)
Mito_stats_104 <- Mito_stats_104[order(Mito_stats_104$'normHits', decreasing = T),]
head(Mito_stats_104)
sink("Mito_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Mito_boruta_104)],NanostringData$Mito))
sink()

# Change the random seed and repeat
set.seed(392)
Mito_boruta_392 <- Boruta(Mito~.,data=NanostringData, doTrace=2)
Mito_stats_392 <- attStats(Mito_boruta_392)
Mito_stats_392 <- Mito_stats_392[order(Mito_stats_392$'normHits', decreasing = T),]
head(Mito_stats_392)
sink("Mito_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Mito_boruta_392)],NanostringData$Mito))
sink()

# Change the random seed and repeat
set.seed(426)
Mito_boruta_426 <- Boruta(Mito~.,data=NanostringData, doTrace=2)
Mito_stats_426 <- attStats(Mito_boruta_426)
Mito_stats_426 <- Mito_stats_426[order(Mito_stats_426$'normHits', decreasing = T),]
head(Mito_stats_426)
sink("Mito_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(Mito_boruta_426)],NanostringData$Mito))
sink()

# Combine results
colnames(Mito_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(Mito_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(Mito_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

Mito_stats <- merge(Mito_stats_104,Mito_stats_392, by = intersect(names(Mito_stats_104),names(Mito_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Mito_stats) <- Mito_stats$'Row.names'
Mito_stats <- Mito_stats[-1]
Mito_stats <- merge(Mito_stats,Mito_stats_426, by = intersect(names(Mito_stats),names(Mito_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(Mito_stats) <- Mito_stats$'Row.names'
Mito_stats <- Mito_stats[-1]
Mito_stats <- Mito_stats[order(Mito_stats$'normHits_104', decreasing = T),]
head(Mito_stats[1:6])

# Export results
write.csv (Mito_stats, file="Mito_Boruta.csv")

#===============================
# Determine the Predictors of AKT-Thr308 Phosphorylation using Boruta
set.seed(104)
pAKT_boruta_104 <- Boruta(pAKT~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
pAKT_stats_104 <- attStats(pAKT_boruta_104)
pAKT_stats_104 <- pAKT_stats_104[order(pAKT_stats_104$'normHits', decreasing = T),]
head(pAKT_stats_104)
sink("pAKT_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(pAKT_boruta_104)],NanostringData$pAKT))
sink()

# Change the random seed and repeat
set.seed(392)
pAKT_boruta_392 <- Boruta(pAKT~.,data=NanostringData, doTrace=2)
pAKT_stats_392 <- attStats(pAKT_boruta_392)
pAKT_stats_392 <- pAKT_stats_392[order(pAKT_stats_392$'normHits', decreasing = T),]
head(pAKT_stats_392)
sink("pAKT_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(pAKT_boruta_392)],NanostringData$pAKT))
sink()

# Change the random seed and repeat
set.seed(426)
pAKT_boruta_426 <- Boruta(pAKT~.,data=NanostringData, doTrace=2)
pAKT_stats_426 <- attStats(pAKT_boruta_426)
pAKT_stats_426 <- pAKT_stats_426[order(pAKT_stats_426$'normHits', decreasing = T),]
head(pAKT_stats_426)
sink("pAKT_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(pAKT_boruta_426)],NanostringData$pAKT))
sink()

# Combine results
colnames(pAKT_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(pAKT_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(pAKT_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

pAKT_stats <- merge(pAKT_stats_104,pAKT_stats_392, by = intersect(names(pAKT_stats_104),names(pAKT_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(pAKT_stats) <- pAKT_stats$'Row.names'
pAKT_stats <- pAKT_stats[-1]
pAKT_stats <- merge(pAKT_stats,pAKT_stats_426, by = intersect(names(pAKT_stats),names(pAKT_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(pAKT_stats) <- pAKT_stats$'Row.names'
pAKT_stats <- pAKT_stats[-1]
pAKT_stats <- pAKT_stats[order(pAKT_stats$'normHits_104', decreasing = T),]
head(pAKT_stats[1:6])

# Export results
write.csv (pAKT_stats, file="pAKT_Boruta.csv")


#===============================
# Determine the Predictors of GR transcriptional activity using Boruta
set.seed(104)
MMTV_luc_boruta_104 <- Boruta(MMTV_luc~.,data=NanostringData, doTrace=2)
# Get the results of the Boruta run
MMTV_luc_stats_104 <- attStats(MMTV_luc_boruta_104)
MMTV_luc_stats_104 <- MMTV_luc_stats_104[order(MMTV_luc_stats_104$'normHits', decreasing = T),]
head(MMTV_luc_stats_104)
sink("MMTV_luc_randomForest_104.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(MMTV_luc_boruta_104)],NanostringData$MMTV_luc))
sink()

# Change the random seed and repeat
set.seed(392)
MMTV_luc_boruta_392 <- Boruta(MMTV_luc~.,data=NanostringData, doTrace=2)
MMTV_luc_stats_392 <- attStats(MMTV_luc_boruta_392)
MMTV_luc_stats_392 <- MMTV_luc_stats_392[order(MMTV_luc_stats_392$'normHits', decreasing = T),]
head(MMTV_luc_stats_392)
sink("MMTV_luc_randomForest_392.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(MMTV_luc_boruta_392)],NanostringData$MMTV_luc))
sink()

# Change the random seed and repeat
set.seed(426)
MMTV_luc_boruta_426 <- Boruta(MMTV_luc~.,data=NanostringData, doTrace=2)
MMTV_luc_stats_426 <- attStats(MMTV_luc_boruta_426)
MMTV_luc_stats_426 <- MMTV_luc_stats_426[order(MMTV_luc_stats_426$'normHits', decreasing = T),]
head(MMTV_luc_stats_426)
sink("MMTV_luc_randomForest_426.txt")
  print(randomForest(NanostringData[,getSelectedAttributes(MMTV_luc_boruta_426)],NanostringData$MMTV_luc))
sink()

# Combine results
colnames(MMTV_luc_stats_104) <- c("meanImp_104", "medianImp_104", "minImp_104", "maxImp_104", "normHits_104", "decision_104")
colnames(MMTV_luc_stats_392) <- c("meanImp_392", "medianImp_392", "minImp_392", "maxImp_392", "normHits_392", "decision_392")
colnames(MMTV_luc_stats_426) <- c("meanImp_426", "medianImp_426", "minImp_426", "maxImp_426", "normHits_426", "decision_426")

MMTV_luc_stats <- merge(MMTV_luc_stats_104,MMTV_luc_stats_392, by = intersect(names(MMTV_luc_stats_104),names(MMTV_luc_stats_392)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(MMTV_luc_stats) <- MMTV_luc_stats$'Row.names'
MMTV_luc_stats <- MMTV_luc_stats[-1]
MMTV_luc_stats <- merge(MMTV_luc_stats,MMTV_luc_stats_426, by = intersect(names(MMTV_luc_stats),names(MMTV_luc_stats_426)),by.x=0, by.y=0, all= FALSE, sort=TRUE)
row.names(MMTV_luc_stats) <- MMTV_luc_stats$'Row.names'
MMTV_luc_stats <- MMTV_luc_stats[-1]
MMTV_luc_stats <- MMTV_luc_stats[order(MMTV_luc_stats$'normHits_104', decreasing = T),]
head(MMTV_luc_stats[1:6])

# Export results
write.csv (MMTV_luc_stats, file="MMTV_luc_Boruta.csv")

## Identifying the minimal set of predictors using randomForest
# Minimal model for Glut4 Translocation
set.seed(392)
minGlut4 <- randomForest(Glut4 ~ Fkbp5c + Socs2 + Bcl2l1 + Tsc22d3 + NCOA1_677_700 + NCOA1_737_759,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minGlut4)
#========================================
# Minimal model for Protein Degradation 
set.seed(392)
minDegradation <- randomForest(Degradation ~ Mito + Socs2,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minDegradation)
#========================================
# Minimal model for GR nuclear translocation
set.seed(392)
minNucTrans <- randomForest(GR_Nuc_Trans ~ PRGC1_134_154 + Fkbp5a + Tsc22d3 + Vav2,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minNucTrans)
#========================================
# Minimal model for Mitochondrial potential
set.seed(392)
minMito <- randomForest(Mito ~ Degradation + Synthesis,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minMito)

#========================================
# Minimal model for GR activity
set.seed(392)
minMMTV_luc <- randomForest(MMTV_luc ~ PAK6_248_270 + EP300_69_91 + NRIP1_173_195 + LCOR_40_62,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minMMTV_luc)

#========================================
# Minimal model for AKT-Thr308 phosphorylation
set.seed(392)
minpAkt <- randomForest(pAKT ~ Synthesis + MAPE_91_113 + NCOR2_2123_2145,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minpAkt)
#========================================
# Minimal model for Protein synthesis
set.seed(392)
minSynthesis <- randomForest(Synthesis ~ CHD9_1023_1045 + NCOR2_2330_2352 + Socs2 + Mito + MAPE_91_113 + Fbxo32 + Sgk1 + Irs1,
                           data=NanostringData,
                           importance=TRUE, 
                           ntree=500, mtry = 1)
# View the predictions
print(minSynthesis)
