---
title: "PCA of GR Ligand-dependent Activity Profiles"
author: "Jerome C. Nwachukwu"
date: "5/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
# Load the package
library(randomForest)
library(Boruta)
library(pheatmap)
library(RColorBrewer)
library(grid)

#Set working directory
setwd("/Volumes/nettleslab/Jerome/Skeletal Muscle Data/Machine_learning/MARCONI/PCA_with_GR_nuc_translocation_data/")
# Load and view the data
NanostringData <-read.csv("GR_data_wo_NR0s.csv", stringsAsFactors=TRUE)
# View(NanostringData)
rownames(NanostringData) <- NanostringData$Compound
NanostringData <- NanostringData[,-1]
NanostringData <- data.frame(scale(NanostringData))

# Cluster each type of feature separately and format the data
HTassays <- NanostringData[,c(1:7)]
Col.order <- hclust(dist(t(HTassays)))$order
HTassays <- HTassays[,Col.order]
HTassays <- cbind(rownames(HTassays), data.frame(HTassays, row.names=NULL))
colnames(HTassays)[colnames(HTassays)=="rownames(HTassays)"] <- "Compounds"
head(HTassays)

Peptides <- NanostringData[,c(8:154)]
Col.order <- hclust(dist(t(Peptides)))$order
Peptides <- Peptides[,Col.order]
Peptides <- cbind(rownames(Peptides), data.frame(Peptides, row.names=NULL))
colnames(Peptides)[colnames(Peptides)=="rownames(Peptides)"] <- "Compounds"
head(Peptides[,c(1:5)])

TargetGenes <- NanostringData[,c(155:187)]
Col.order <- hclust(dist(t(TargetGenes)))$order
TargetGenes <- TargetGenes[,Col.order]
TargetGenes <- cbind(rownames(TargetGenes), data.frame(TargetGenes, row.names=NULL))
colnames(TargetGenes)[colnames(TargetGenes)=="rownames(TargetGenes)"] <- "Compounds"
head(TargetGenes[,c(1:5)])

# Re-combine the datasets
myData <- merge(HTassays, Peptides, by = intersect(names(HTassays),names(Peptides)), by.x= 'Compounds', by.y= 'Compounds', all= FALSE, sort=TRUE)
myData <- merge(myData, TargetGenes, by = intersect(names(myData),names(TargetGenes)), by.x= 'Compounds', by.y= 'Compounds', all= FALSE, sort=TRUE)
row.names(myData) <- myData$Compounds
NanostringData <- myData[,-1]
head(NanostringData[,c(1:6)])
#=============================
## Principal component analysis (PCA)
#principal component analysis
prin_comp_zscore <- prcomp(NanostringData, scale. = T)
# names(prin_comp_zscore)
# outputs the mean of variables
#prin_comp_zscore$center
# write.csv(prin_comp_zscore$center, file="PCA_center_mean.csv")
# outputs the standard deviation of variables
# prin_comp_zscore$scale
# write.csv(prin_comp_zscore$scale, file="PCA_scale_stdev.csv")
# The rotation measure provides the principal component loading. 
# Each column of rotation matrix contains the principal component loading vector. 
# This is the most important measure we should be interested in.
write.csv (prin_comp_zscore$rotation, file="PCA_rotation.csv")
#dim(prin_comp_zscore$x)
#plot the resultant principal components.
#biplot(prin_comp_zscore, scale = 0)
#compute standard deviation of each principal component
std_dev_zscore <- prin_comp_zscore$sdev
#compute variance
pr_var_zscore <- std_dev_zscore^2
#proportion of variance explained (in percent)
prop_varex_zscore <- 100*pr_var_zscore/sum(pr_var_zscore)
write.csv (cumsum(prop_varex_zscore), file="PCA_varex.csv")
write.csv (prop_varex_zscore, file="PCA_varex2.csv")

#=============================
library("scatterplot3d")
scatterplot3d(NanostringData$Glut4,y=NanostringData$NCOR2_2330_2352, z=NanostringData$IKBB_62_84,,
              xlab = "Glut4 Translocation", zlab = "IKKB_62_84", ylab = "NCOR2_2330_2352",grid = F,box = T, angle=24)



